---
title: "data_manipulation"
author: "Apoorva Srinivasan"
date: "10/1/2018"
output: github_document
---


```



```{r}
library(tidyverse)
library(readr)
options(tibble.print_min = 3)

litters_data = read_csv("./data/FAS_litters.csv",
  col_types = "ccddiiii")
litters_data = janitor::clean_names(litters_data)

pups_data = read_csv("./data/FAS_pups.csv",
  col_types = "ciiiii")
pups_data = janitor::clean_names(pups_data)

```


Selecting variables

```{r}
select(litters_data, group, litter_number, gd0_weight)
```

using select helpers

```{r}
select(litters_data, starts_with("gd"))
```

```{r}
select(pups_data, litter_number,pd_ears)
```

```{r}
filter(litters_data, pups_born_alive %in% 4:7, !is.na(gd0_weight))
```


```{r}
mutate(litters_data, wt_gain = gd18_weight - gd0_weight)
```

```{r}
mutate(pups_data, subtract = pd_pivot - 7)
```

```{r}
    read_csv("./data/FAS_pups.csv"  , col_types = "ciiiii") %>% 
  janitor ::clean_names() %>%
  filter(sex == 1)%>%
  select(-pd_ears)%>%
  mutate(variable_subtract = pd_pivot - 7)
  
``

